Make any stupid plot you want

### 2020-10-15 draft/intro.tex
:shrugs: dunno what changed

Steven's measurement scales have the following structure \cite{stevensTheoryScalesMeasurement1946}:
%the big point of disagreement on the scales seems to be the stats column that we don't care about
\begin{table}
    \begin{tabular}{l l l l}
        nominal & permutation group & one to one substitutions & $=, \neq $\\
        ordinal & isotonic group & monotonic increasing functions &  $=, \neq $, $\leq, \geq$\\
        interval & general linear group & matrix operations &  $=, \neq, \leq, \geq, +, -, $\\
        ratio & similarity group & $ \mathbb{Z}^+ $ & 
    \end{tabular}
\end{table}

@@

%% distance along edge to transformed physical space, s function 
%% colormap_nrom - t: d \mapsto RGBA, continouts t: d(s) \mapsto 
%% 1d has to be parameterized  t: d(s), really want t: d\ mapsto RGBA
%%  d(s) \mapsto {d....} on interval [s_{0}..s_{n}]
%% flip this to the otherside so it's an adjacency matrix
%% how do we represent invariance/equivariance  A: D \mapsto \I
%% D - columns + topology (section + topology)
%% artist is the visual idiom 
%% {D cartesian product Tau} \mapsto I
%% Artist already has everything in VV space and composing into idiom
%% functions on simplex crossed wuth transformers - everything in visual space w/ same topology
%% A: visual \mapsto idiom
%% Artist (raw data + transforms )
%% carry topology over from VV space to I space -> singular CW complex 
%% (has no inherent structure) 
%% invaraince - shuffle_sq on tick labels = shuffle_sq on data 
%% how do you preserve invariance on topology->Idiom?
%% \tau_{2} is a new \tau function taht's really tau + 2
%% taus is a group of transform functions under composition 
%% tau gos data to visual variable
%% group of functions + 
%% measurement space groups is what class of functions don't destroy your data
%% \tau: d \mapsto vv - group of mapto functions
%% set of allowable \tau is where symmtery d/v are preserved 
%% d\v isomorphisms where tau takes you from one to another
%% d\v is  isomorphisms under group of taus where tau is the permutation group
%%
%% math: structure is same as type

\begin{table}
    \label{tab:taus}
    \begin{tabular}{l*{6}{c}} 
                              & position &  size  & shape & texture & color hue & color value  \\
    nominal                   & $\tau$   & $\tau$ & $\tau$& $\tau$  & $\tau$    & $\tau$       \\
    ordinal                   & $\tau$   & $\tau$ &       &         &           & $\tau$  \\
    interval                  & $\tau$   & $\tau$ &       &         &           & $\tau$  \\
    ratio                     & $\tau$   & $\tau$ &       &         &           & $\tau$ \\  
    \end{tabular}
\caption{Group of $\{t_{1}....t_{n}\}$ where $tau: d \mapsto v$ preserving equivariance such that $d$ and $v$ are isomorphic. $d$ is data of type \{nominal, ordinal, interval, ratio\} and $v$ are the visual channels. \cite{bertinIIPropertiesGraphic2011,munznerMarksChannels}}
\end{table}

@@

>>>>

@@

%% distance along edge to transformed physical space, s function 
%% colormap_nrom - t: d \mapsto RGBA, continouts t: d(s) \mapsto 
%% 1d has to be parameterized  t: d(s), really want t: d\ mapsto RGBA
%%  d(s) \mapsto {d....} on interval [s_{0}..s_{n}]
%% flip this to the otherside so it's an adjacency matrix
%% how do we represent invariance/equivariance  A: D \mapsto \I
%% D - columns + topology (section + topology)
%% artist is the visual idiom 
%% {D cartesian product Tau} \mapsto I
%% Artist already has everything in VV space and composing into idiom
%% functions on simplex crossed wuth transformers - everything in visual space w/ same topology
%% A: visual \mapsto idiom
%% Artist (raw data + transforms )
%% carry topology over from VV space to I space -> singular CW complex 
%% (has no inherent structure) 
%% invaraince - shuffle_sq on tick labels = shuffle_sq on data 
%% how do you preserve invariance on topology->Idiom?
%% \tau_{2} is a new \tau function taht's really tau + 2
%% taus is a group of transform functions under composition 
%% tau gos data to visual variable
%% group of functions + 
%% measurement space groups is what class of functions don't destroy your data
%% \tau: d \mapsto vv - group of mapto functions
%% set of allowable \tau is where symmtery d/v are preserved 
%% d\v isomorphisms where tau takes you from one to another
%% d\v is  isomorphisms under group of taus where tau is the permutation group
%%
%% math: structure is same as type
Steven's measurement scales have the following structure \cite{stevensTheoryScalesMeasurement1946}:
%the big point of disagreement on the scales seems to be the stats column that we don't care about
\begin{table}
    \lable{tab:measument_type}
    \begin{tabular}{l l l l}
        nominal & permutation group & one to one substitutions & $=, \neq $\\
        ordinal & isotonic group & monotonic increasing functions &  $=, \neq $, $\leq, \geq$\\
        interval & general linear group & matrix operations &  $=, \neq, \leq, \geq, +, -, $\\
        ratio & similarity group & $ \mathbb{Z}^+ $ & 
    \end{tabular}
\end{table}

%%% make a second table later of what MPL currently supports
%%% redraw as graph
%%% set of all possible taus (operations can possibly be defined on both sides)

Split is discrete/ vs continous measurment types 
It is possible to write taus to ....

A: (v...v) -> I
%% tau is when we have data/visual lineups for labeling colorbar \ legend
%% colorbar vs. legend - continous vs discrete

\begin{table}
    \label{tab:taus}
    \begin{tabular}{l*{6}{c}} 
                              & position      &  size        & shape        & texture     & color \\
    nominal                   &  1            &  1           & 1            & 1           & 1     \\ 
    ordinal                   &  1            &  1           & 1            & 1           & 1     \\
    interval                  &  1            &  1           &              &             & 1     \\   
    ratio                     &  1            &  1           &              &             & 1     \\  
    \end{tabular}
\caption{Group of $\{t_{1}....t_{n}\}$ where $tau: d \mapsto v$ preserving equivariance such that $d$ and $v$ are isomorphic. $d$ is data of type \{nominal, ordinal, interval, ratio\} and $v$ are the visual channels. \cite{bertinIIPropertiesGraphic2011,munznerMarksChannels}}
\end{table}

@@

%%% draw what the function graph looks like for scatter versus linesg
Scatter Plot:
K - 0D disconnected points
\begin{multline}
A: (C1, C2, C3...)\mapsto (M....)\\
t \in A 
\end{multline}
